---
title: "Solve_LIMS_cleaned"
output: html_document
date: "2025-01-15"
---

```{r LIM SET UP, include = F, warning=F}
library(LIM)
library(DT)
library(NetIndices)
library(dplyr)
library(ggpubr)
require(resample)
library(gridExtra)
library(matrixStats)
library(patchwork)
library(samplelim)
library(autoLIMR)
library(igraph)
library(tidyr)
source("functions/calculate_LIM_indices.R")
source("functions/network_indices.R")
source("functions/sample_save_Lims.R")
#load("LIM_data.Rdata")

```

#LIM set up and validity of the solution
```{r}
############################ 2009 ##########################
# File path for 2009 data
abrilfw09 <- "Input_files_LIM/FW_2009_bact.txt"
abrilfw12 <- "Input_files_LIM/FW_2012_bact.txt"
abrilfw16 <- "Input_files_LIM/FW_2016_bact.txt"
abrilfw19 <- "Input_files_LIM/FW_2019_bact.txt"
abrilfw22 <- "Input_files_LIM/FW_2022_bact.txt"

# Read data
readLIM.abril09 <- LIM::Read(file = abrilfw09, verbose = TRUE, checkLinear = TRUE)
readLIM.abril12 <- LIM::Read(file = abrilfw12, verbose = TRUE, checkLinear = TRUE)
readLIM.abril16 <- LIM::Read(file = abrilfw16, verbose = TRUE, checkLinear = TRUE)
readLIM.abril19 <- LIM::Read(file = abrilfw19, verbose = TRUE, checkLinear = TRUE)
readLIM.abril22 <- LIM::Read(file = abrilfw22, verbose = TRUE, checkLinear = TRUE)


LIM.abril09 <- Setup(readLIM.abril09)
LIM.abril12 <- Setup(readLIM.abril12)
LIM.abril16 <- Setup(readLIM.abril16)
LIM.abril19 <- Setup(readLIM.abril19)
LIM.abril22 <- Setup(readLIM.abril22)

# Calculate solution and check validity of the solution
Solldeiabril09 <- Ldei(LIM.abril09, verbose = TRUE)
#Rangesabril09 <- lim.ranges(LIM.abril09)
any((LIM.abril09$A %*% Solldeiabril09$X - LIM.abril09$B) > 1e-8)
any((LIM.abril09$G %*% Solldeiabril09$X - LIM.abril09$H) < (-1e-8))

Solldeiabril12 <- Ldei(LIM.abril12, verbose = TRUE)
#Rangesabril12 <- lim.ranges(LIM.abril12)
any((LIM.abril12$A %*% Solldeiabril12$X - LIM.abril12$B) > 1e-8)
any((LIM.abril12$G %*% Solldeiabril12$X - LIM.abril12$H) < (-1e-8))

Solldeiabril16 <- Ldei(LIM.abril16, verbose = TRUE)
#Rangesabril16 <- lim.ranges(LIM.abril16)
any((LIM.abril16$A %*% Solldeiabril16$X - LIM.abril16$B) > 1e-8)
any((LIM.abril16$G %*% Solldeiabril16$X - LIM.abril16$H) < (-1e-8))

Solldeiabril19 <- Ldei(LIM.abril19, verbose = TRUE)
#Rangesabril19 <- lim.ranges(LIM.abril19)
any((LIM.abril19$A %*% Solldeiabril19$X - LIM.abril19$B) > 1e-8)
any((LIM.abril19$G %*% Solldeiabril19$X - LIM.abril19$H) < (-1e-8))

Solldeiabril22 <- Ldei(LIM.abril22, verbose = TRUE)
#Rangesabril22 <- lim.ranges(LIM.abril22)
any((LIM.abril22$A %*% Solldeiabril22$X - LIM.abril22$B) > 1e-8)
any((LIM.abril22$G %*% Solldeiabril22$X - LIM.abril22$H) < (-1e-8))

# Plot web diagram, change according to the year you want to plot
diagram::plotweb(Flowmatrix(lim = LIM.abril19, web = Solldeiabril19$X + 1),
  bty = "n", lab.size = 0.6, log = TRUE, leg.title = "log + 1"
)

```

#Sample LIM solutions

Not running because this process is intense and a HPC is needed.
```{r, eval = F}
LIMs <- list(
abril16 = LIM.abril16,
abril09 = LIM.abril09,
abril12 = LIM.abril12,
abril22 = LIM.abril22)
abril19 = LIM.abril19)   

output_directory <- "code"

calculate_and_save_batches(LIMs, output_directory, nsamp_total =1800, batch_size =1800)
```

#Load the results from the LIM repetitions
```{r}
load("Results_sample_LIM/results_2009.Rdata")
load("Results_sample_LIM/results_2012.Rdata")
load("Results_sample_LIM/results_2016.Rdata")
load("Results_sample_LIM/results_2019.Rdata")
load("Results_sample_LIM/results_2022.Rdata")
```

#Visualize flow ranges
```{r, fig.height=10, fig.width=6}
par(mfrow=c(2,2))

RangeVal_LIM_abril09 <- sort(Rangesabril09[,2] - Rangesabril09[,1])
plot(cbind(RangeVal_LIM_abril09), axes=FALSE, xlab="", ylab="", main="Flow ranges - LIM.abril09", log="")
axis(1, at=1:length(RangeVal_LIM_abril09), labels=names(RangeVal_LIM_abril09), las=2, cex.axis=1)
axis(2, las=2)

RangeVal_LIM_abril12 <- sort(Rangesabril12[,2] - Rangesabril12[,1])
plot(cbind(RangeVal_LIM_abril12), axes=FALSE, xlab="", ylab="", main="Flow ranges - LIM.abril12", log="")
axis(1, at=1:length(RangeVal_LIM_abril12), labels=names(RangeVal_LIM_abril12), las=2, cex.axis=1)
axis(2, las=2)

RangeVal_LIM_abril16 <- sort(Rangesabril16[,2] - Rangesabril16[,1])
plot(cbind(RangeVal_LIM_abril16), axes=FALSE, xlab="", ylab="", main="Flow ranges - LIM.abril16", log="")
axis(1, at=1:length(RangeVal_LIM_abril16), labels=names(RangeVal_LIM_abril16), las=2, cex.axis=1)
axis(2, las=2)

RangeVal_LIM_abril19 <- sort(Rangesabril19[,2] - Rangesabril19[,1])
plot(cbind(RangeVal_LIM_abril19), axes=FALSE, xlab="", ylab="", main="Flow ranges - LIM.abril19", log="")
axis(1, at=1:length(RangeVal_LIM_abril19), labels=names(RangeVal_LIM_abril19), las=2, cex.axis=1)
axis(2, las=2)

RangeVal_LIM_abril22 <- sort(Rangesabril22[,2] - Rangesabril22[,1])
plot(cbind(RangeVal_LIM_abril22), axes=FALSE, xlab="", ylab="", main="Flow ranges - LIM.abril22", log="")
axis(1, at=1:length(RangeVal_LIM_abril22), labels=names(RangeVal_LIM_abril22), las=2, cex.axis=1)
axis(2, las=2)

```


#Calculate the variables for each repetition

**Resp:** Value of the flow going to DIC **Uptake:** All flows going to that compartment **Assimilation:** Uptake minus the flows going to detritus.
**Production:** Assimilation minus respiration

```{r, echo = F, fig.width=13, fig.height=10, include = F}

# Create a matrix with rows as number of variables, and columns as number of repetitons (to store the variables of each repetition and afterwards make stats)
Var_2009 <- matrix(NA, 
                             nrow = LIM.abril09$NVariables,
                             ncol = nrow(results_2009),
                             dimnames = list(LIM.abril09$Variables, 
                                             1:nrow(results_2009)))

for (i in 1:nrow(results_2009)) {
    Var_2009[, i] <- Variables(LIM.abril09, results_2009[i, ])$values
}

mean_sd_2009 <- t(apply(Var_2009, 1, function(x) c(mean(x, na.rm = TRUE), sd(x, na.rm = TRUE)))) #calculate mean and standard deviation for each variable

results_2009_stats <- data.frame(
  mean = round(mean_sd_2009[, 1], 4),
  sd = round(mean_sd_2009[, 2], 4),
  row.names = rownames(Var_2009)
)

# Rename columns
colnames(results_2009_stats) <- c("mean_2009", "sd_2009")

# Repeat for other years
Var_2012 <- matrix(NA, 
                             nrow = LIM.abril12$NVariables,
                             ncol = nrow(results_2012),
                             dimnames = list(LIM.abril12$Variables, 
                                             1:nrow(results_2012)))

for (i in 1:nrow(results_2012)) {
    Var_2012[, i] <- Variables(LIM.abril12, results_2012[i, ])$values
}

mean_sd_2012 <- t(apply(Var_2012, 1, function(x) c(mean(x, na.rm = TRUE), sd(x, na.rm = TRUE))))

results_2012_stats <- data.frame(
  mean = round(mean_sd_2012[, 1], 4),
  sd = round(mean_sd_2012[, 2], 4),
  row.names = rownames(Var_2012)
)

# Rename columns
colnames(results_2012_stats) <- c("mean_2012", "sd_2012")

# 2016
Var_2016 <- matrix(NA, 
                             nrow = LIM.abril16$NVariables,
                             ncol = nrow(results_2016),
                             dimnames = list(LIM.abril16$Variables, 
                                             1:nrow(results_2016)))

for (i in 1:nrow(results_2016)) {
    Var_2016[, i] <- Variables(LIM.abril16, results_2016[i, ])$values
}

mean_sd_2016 <- t(apply(Var_2016, 1, function(x) c(mean(x, na.rm = TRUE), sd(x, na.rm = TRUE))))

results_2016_stats <- data.frame(
  mean = round(mean_sd_2016[, 1], 5),
  sd = round(mean_sd_2016[, 2], 5),
  row.names = rownames(Var_2016)
)

# Rename columns
colnames(results_2016_stats) <- c("mean_2016", "sd_2016")


# 2019
Var_2019 <- matrix(NA, 
                             nrow = LIM.abril19$NVariables,
                             ncol = nrow(results_2019),
                             dimnames = list(LIM.abril19$Variables, 
                                             1:nrow(results_2019)))

for (i in 1:nrow(results_2019)) {
    Var_2019[, i] <- Variables(LIM.abril19, results_2019[i, ])$values
}

mean_sd_2019 <- t(apply(Var_2019, 1, function(x) c(mean(x, na.rm = TRUE), sd(x, na.rm = TRUE))))

results_2019_stats <- data.frame(
  mean = round(mean_sd_2019[, 1], 4),
  sd = round(mean_sd_2019[, 2], 4),
  row.names = rownames(Var_2019)
)

 # 2022
Var_2022 <- matrix(NA, 
                             nrow = LIM.abril22$NVariables,
                             ncol = nrow(results_2022),
                             dimnames = list(LIM.abril22$Variables, 
                                             1:nrow(results_2022)))

for (i in 1:nrow(results_2022)) {
    Var_2022[, i] <- Variables(LIM.abril22, results_2022[i, ])$values
}

# Apply the function to each row of the matrix (x represents the row values, Margin = 1).
# For each row, calculate the mean and standard deviation, ignoring NA values.
mean_sd_2022 <- t(apply(Var_2022, 1, function(x) c(mean(x, na.rm = TRUE), sd(x, na.rm = TRUE))))

results_2022_stats <- data.frame(
  mean = round(mean_sd_2022[, 1], 4),
  sd = round(mean_sd_2022[, 2], 4),
  row.names = rownames(Var_2022)
)

# Rename columns
colnames(results_2022_stats) <- c("mean_2022", "sd_2022") 

```

#Production and flows plot
```{r}
# =============================
# Prepare turbine variables plot ----
# =============================

selected_variables <- c("FlowsTOTR", "FlowsFROMTR", "ProdTURBINEROCK", "SeconProd", 
                        "TurbineTotal", "TotalRESP", "TotalUpta", "UptaTURBINEROCK")

extract_year_stats <- function(stats, year) {
  df <- stats[selected_variables, ]
  colnames(df) <- c("mean", "sd")
  df$year <- year
  df$variable <- selected_variables
  df
}

combined_data <- bind_rows(
  extract_year_stats(results_2009_stats, 2009),
  extract_year_stats(results_2012_stats, 2012),
  extract_year_stats(results_2016_stats, 2016),
  extract_year_stats(results_2019_stats, 2019),
  extract_year_stats(results_2022_stats, 2022)
)

combined_data$variable <- factor(combined_data$variable, levels = selected_variables)

# Define patterns to exclude flows we don’t want in totals
exclude_patterns <- c("->DIC", "->EXP", "->BUR", "DIC->PHY", "EXP->", "BUR->", "DIC->")

# Filter out unwanted flows
filtered_2009 <- results_2009[, !grepl(paste(exclude_patterns, collapse = "|"), colnames(results_2009))]
filtered_2012 <- results_2012[, !grepl(paste(exclude_patterns, collapse = "|"), colnames(results_2012))]
filtered_2016 <- results_2016[, !grepl(paste(exclude_patterns, collapse = "|"), colnames(results_2016))]
filtered_2019 <- results_2019[, !grepl(paste(exclude_patterns, collapse = "|"), colnames(results_2019))]
filtered_2022 <- results_2022[, !grepl(paste(exclude_patterns, collapse = "|"), colnames(results_2022))]

# Calculate total internal flows
total_flows_stats <- data.frame(
  mean = c(mean(rowSums(filtered_2009)), mean(rowSums(filtered_2012)), mean(rowSums(filtered_2016)),
           mean(rowSums(filtered_2019)), mean(rowSums(filtered_2022))),
  sd = c(sd(rowSums(filtered_2009)), sd(rowSums(filtered_2012)), sd(rowSums(filtered_2016)),
         sd(rowSums(filtered_2019)), sd(rowSums(filtered_2022))),
  year = c(2009, 2012, 2016, 2019, 2022),
  variable = "Total Flows"
)

# Extract turbine flows from combined_data (calculated in earlier section)
flows_to_turbine <- combined_data %>% filter(variable == "TurbineTotal")

# Calculate non-turbine internal flows
non_turbine_flows_stats <- total_flows_stats
non_turbine_flows_stats$mean <- total_flows_stats$mean - flows_to_turbine$mean
non_turbine_flows_stats$variable <- "Non-Turbine Flows"

# Combine for plotting
combined_plot_data <- bind_rows(non_turbine_flows_stats, flows_to_turbine)

# Set factor levels to control stacking
combined_plot_data$variable <- factor(combined_plot_data$variable, levels = c("Non-Turbine Flows", "TurbineTotal"))

# Calculate % contribution of turbine flows
flows_to_turbine$percentage <- (flows_to_turbine$mean / total_flows_stats$mean) * 100
combined_plot_data$label <- ifelse(combined_plot_data$variable == "TurbineTotal",
                                   paste0(round(flows_to_turbine$percentage, 1), "%"),
                                   "")

# Format
combined_plot_data$year <- factor(combined_plot_data$year)
combined_plot_data$variable <- factor(combined_plot_data$variable, levels = c("Non-Turbine Flows","TurbineTotal"))

# Plot
col_palette <- c("Non-Turbine Flows" = "#377EB8", "TurbineTotal" = "#FF7F00")

turbine_variables_plot <- ggplot(combined_plot_data, aes(x = year, y = mean, fill = variable)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd),
                width = 0.2, position = position_dodge(width = 0.8), color = "black") +
  geom_text(data = combined_plot_data %>% filter(variable == "TurbineTotal"),
            aes(label = label, y = mean + sd + 8),
            position = position_dodge(width = 0.8),
            size = 4, fontface = "bold", hjust = -0.2) +
  scale_fill_manual(values = col_palette,
                    labels = c("TurbineTotal" = "Hard-substrate fauna flows",
                               "Non-Turbine Flows" = "Internal flows")) +
  labs(title = expression("Internal flows and flows to hard-substrate community"),
       x = "Year",
       y = expression("Mean carbon flows (mmol C / m"^2*"/day)"),
       fill = "Flow Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.position = "bottom")


# =============================
# Prepare production plot ----
# =============================

prod_vars <- c("SeconProd", "ProdTURBINEROCK")

extract_prod_stats <- function(stats, year) {
  df <- stats[prod_vars, ]
  colnames(df) <- c("mean", "sd")
  df$year <- year
  df$variable <- prod_vars
  df
}

prod_data <- bind_rows(
  extract_prod_stats(results_2009_stats, 2009),
  extract_prod_stats(results_2012_stats, 2012),
  extract_prod_stats(results_2016_stats, 2016),
  extract_prod_stats(results_2019_stats, 2019),
  extract_prod_stats(results_2022_stats, 2022)
)

# Rename variables
prod_data$variable <- as.character(prod_data$variable)
prod_data$variable[prod_data$variable == "SeconProd"] <- "Secondary Production"
prod_data$variable[prod_data$variable == "ProdTURBINEROCK"] <- "Hard-substrate fauna production"
prod_data$variable <- factor(prod_data$variable, levels = c("Hard-substrate fauna production", "Secondary Production"))

# Calculate remaining secondary production
turbo <- prod_data %>% filter(variable == "Hard-substrate fauna production")
sec <- prod_data %>% filter(variable == "Secondary Production")

remaining_sec <- sec
remaining_sec$mean <- sec$mean - turbo$mean
remaining_sec$sd <- sqrt(sec$sd^2 + turbo$sd^2)
remaining_sec$variable <- "Remaining Secondary Production"

# Combine and recode factor levels
combined_prod <- bind_rows(turbo, remaining_sec)
#combined_prod$variable <- factor(combined_prod$variable,
 #                                levels = c("Remaining Secondary Production", "Hard-substrate production"))

# Calculate turbine % and labels
combined_prod <- combined_prod %>%
  group_by(year) %>%
  mutate(total = sum(mean),
         percentage = if_else(variable == "Hard-substrate fauna production", mean / total * 100, NA_real_),
         label = if_else(!is.na(percentage), paste0(round(percentage, 1), "%"), "")
  )

combined_prod$variable <- factor(combined_prod$variable,
                                 levels = c("Remaining Secondary Production", "Hard-substrate fauna production"))


# Production plot
col_palette_prod <- c(                      "Remaining Secondary Production" = "#4DAF4A",
                                            "Hard-substrate fauna production" = "#FF7F00" 
)

production_plot <- ggplot(combined_prod, aes(x = factor(year), y = mean, fill = variable)) +
  geom_bar(stat = "identity", position = position_dodge(0.8)) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd),
                width = 0.2, position = position_dodge(0.8)) +
  geom_text(
    data = combined_prod %>% filter(variable == "Hard-substrate fauna production"),
    aes(label = label, y = mean + sd + 0.7),
    position = position_dodge(0.8),
    size = 4, fontface = "bold", hjust = -0.2
  ) +
  scale_fill_manual(values = col_palette_prod) +
  labs(
    title = "Secondary and hard-substrate fauna production",
    x = "Year",
    y = expression("Mean production (mmol C / m"^2*"/day)"),
    fill = "Production Type"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.text = element_text(size = 14),
    plot.title = element_text(hjust = 0.5, size = 14),
    legend.position = "bottom"
  )

production_plot

turbine_variables_plot

```


```{r, eval = F}
# Calculate indices for each year and type
GenInd09 <- calculate_indices(LIM.abril09, results_2009, "2009", "gen")
GenInd12 <- calculate_indices(LIM.abril12, results_2012, "2012", "gen")
GenInd16 <- calculate_indices(LIM.abril16, results_2016, "2016", "gen")
GenInd19 <- calculate_indices(LIM.abril19, results_2019, "2019", "gen")
GenInd22 <- calculate_indices(LIM.abril22, results_2022, "2022", "gen")

# Calculate indices for each year and type
PathInd09 <- calculate_indices(LIM.abril09, results_2009, "2009", "path")
PathInd12 <- calculate_indices(LIM.abril12, results_2012, "2012", "path")
PathInd16 <- calculate_indices(LIM.abril16, results_2016, "2016", "path")
PathInd19 <- calculate_indices(LIM.abril19, results_2019, "2019", "path")
PathInd22 <- calculate_indices(LIM.abril22, results_2022, "2022", "path")
```

```{r}
load("Results_sample_LIM/Network_Indices.Rdata")
```

#Quantitative indices plotting
```{r}
# Define color palette
col_palette <- RColorBrewer::brewer.pal(9, "Set1")

# Combine data for all years
PathIndices_all <- bind_rows(PathInd09, PathInd12, PathInd16, PathInd19, PathInd22)
GenIndices_all <- bind_rows(GenInd09, GenInd12, GenInd16, GenInd19, GenInd22)

# Reshape data to long format and clean
PathIndices_long <- PathIndices_all %>%
  pivot_longer(cols = -c(Network, Iteration), names_to = "Index", values_to = "Value") %>%
  mutate(Value = as.numeric(Value)) %>%
  filter(!is.na(Value), Index == "FCIb")  # Only keep FCIb

GenIndices_long <- GenIndices_all %>%
  pivot_longer(cols = -c(Network, Iteration), names_to = "Index", values_to = "Value") %>%
  mutate(Value = as.numeric(Value)) %>%
  filter(!is.na(Value), Index == "T..")  # Only keep T..

# Plot: General Indices with Confidence Interval (Boxplot)
GenPlot_with_CI <- ggplot(GenIndices_long, aes(x = Network, y = Value, fill = Network)) +
  geom_boxplot(outlier.size = 2, outlier.colour = "red", alpha = 0.7) +
  labs(title = "Total system throughput (T..)",
       x = "Year",
       y = expression("T.. (mmol C / m"^2*"/day)"),
       fill = "Year") +
  scale_fill_manual(values = col_palette) +
  theme_bw() +
  theme(axis.text.x = element_text(hjust = 1),
        strip.text = element_text(size = 10),
        panel.background = element_blank(),
        plot.background = element_blank())

# Plot: Pathway Indices with Confidence Interval (Boxplot)
PathPlot_with_CI <- ggplot(PathIndices_long, aes(x = Network, y = Value, fill = Network)) +
  geom_boxplot(outlier.size = 2, outlier.colour = "red", alpha = 0.7) +
  labs(title = "Finn Cycling Index (FCIb)",
       x = "Year",
       y = "Value",
       fill = "Year") +
  scale_fill_manual(values = col_palette) +
  theme_bw() +
  theme(axis.text.x = element_text(hjust = 1),
        strip.text = element_text(size = 10),
        panel.background = element_blank(),
        plot.background = element_blank())

# Display plots
GenPlot_with_CI
PathPlot_with_CI

```




#Interaction strenght
```{r, warning = F}

col_palette <- RColorBrewer::brewer.pal(9, "Set2")

FM_2009 = LIM::Flowmatrix(LIM.abril09, web = colMeans(results_2009))
FM_2012 = LIM::Flowmatrix(LIM.abril12, web = colMeans(results_2012))
FM_2016 = LIM::Flowmatrix(LIM.abril16, web = colMeans(results_2016))
FM_2019 = LIM::Flowmatrix(LIM.abril19, web = colMeans(results_2019))
FM_2022 = LIM::Flowmatrix(LIM.abril22, web = colMeans(results_2022))

link_weights_2009 <- calculate_link_weights_distribution(FM_2009, results_2009, "2009")
link_weights_2012 <- calculate_link_weights_distribution(FM_2012, results_2012, "2012")
link_weights_2016 <- calculate_link_weights_distribution(FM_2016, results_2016, "2016")
link_weights_2019 <- calculate_link_weights_distribution(FM_2019, results_2019, "2019")
link_weights_2022 <- calculate_link_weights_distribution(FM_2022, results_2022, "2022")

# Combine results from all years
link_weights_all <- bind_rows(link_weights_2009, link_weights_2012, link_weights_2016, link_weights_2019, link_weights_2022)

# Summary and plotting
# Calculate summary statistics across all years
summary_stats <- link_weights_all %>%
  group_by(Network) %>%
  summarise(
    Mean_of_Mean_Link_Weight = mean(Mean_Link_Weight),
    Variance_of_Link_Weight = mean(Variance_Link_Weight),
    Mean_SD_Link_Weight = mean(SD_Link_Weight)
  )

# Print summary statistics
print(summary_stats)

#write.csv(summary_stats, "~/phD/WP1_TemporalFW/LIM/interaction_Strenght_stats_Results.csv")

# Plot the distribution of link weights across years
IS = ggplot(link_weights_all, aes(x = Mean_Link_Weight, fill = Network)) +
  facet_wrap(~ Network, scales = "free") +
  scale_fill_manual(values = col_palette) + 
  geom_histogram(bins = 30, position = "dodge", alpha = 0.7) +
  labs(title = "Interaction strength",
       x = expression("mmol C / m"^2*"/day"),
       y = "Frequency") +
  theme_minimal() + 
  theme(axis.text.x = element_text(hjust = 1),
        strip.text = element_text(size = 10), 
        panel.background = element_blank(), 
        plot.background = element_blank())

col_palette <- RColorBrewer::brewer.pal(9, "Set1")

# Calcular para cada red y combinar resultados
df_list <- list(
  calculate_link_weights_distribution2(FM_2009, results_2009, "2009"),
  calculate_link_weights_distribution2(FM_2012, results_2012, "2012"),
  calculate_link_weights_distribution2(FM_2016, results_2016, "2016"),
  calculate_link_weights_distribution2(FM_2019, results_2019, "2019"),
  calculate_link_weights_distribution2(FM_2022, results_2022, "2022")
)

link_weights_all <- bind_rows(df_list)

# Calcular medias por año para anotar en el plot
mean_values <- link_weights_all %>%
  group_by(Network) %>%
  summarize(Mean_Link_Weight = mean(Mean_Link_Weight),
            Variance_link_weight =  mean(Variance_Link_Weight)) 


# Boxplot de la varianza de los pesos de enlace con anotaciones de media
variance_IS <- ggplot(link_weights_all, aes(x = Network, y = Variance_Link_Weight, fill = Network)) +
  geom_boxplot(outlier.size = 2, outlier.colour = "red", alpha = 0.7) +
#  geom_text(data = mean_values, aes(label = round(Mean_Link_Weight, 3), y = max(link_weights_all$Variance_Link_Weight) *0.9),
    #        position = position_dodge(width = 0.95), size = 5, vjust = -0.2) +
  labs(title = "Interaction strength (IS)",
       x = "Year",
       y = expression("IS (mmol C / m"^2*"/day)"),
       fill = "Year") +
  scale_fill_manual(values = col_palette, "paired") +
  theme_bw() +
  theme(axis.text.x = element_text(hjust = 1),
        strip.text = element_text(size = 10), 
        panel.background = element_blank(), 
        plot.background = element_blank())

```


# Summary statistics
```{r}
# Compute statistics for T..
T_summary <- GenIndices_long %>%
  group_by(Network) %>%
  summarize(
    Q1 = quantile(Value, 0.25, na.rm = TRUE),
    Median = median(Value, na.rm = TRUE),
    Q3 = quantile(Value, 0.75, na.rm = TRUE),
    IQR = Q3 - Q1,
    Variance = var(Value, na.rm = TRUE)
  )

# Compute statistics for FCIb
FCIb_summary <- PathIndices_long %>%
  group_by(Network) %>%
  summarize(
    Q1 = quantile(Value, 0.25, na.rm = TRUE),
    Median = median(Value, na.rm = TRUE),
    Q3 = quantile(Value, 0.75, na.rm = TRUE),
    IQR = Q3 - Q1,
    Variance = var(Value, na.rm = TRUE)
  )

IS_summary <- link_weights_all %>%
  group_by(Network) %>%
  summarize(
    Q1 = quantile(Variance_Link_Weight, 0.25, na.rm = TRUE),
    Median = median(Variance_Link_Weight, na.rm = TRUE),
    Q3 = quantile(Variance_Link_Weight, 0.75, na.rm = TRUE),
    IQR = Q3 - Q1,
    Variance = var(Variance_Link_Weight, na.rm = TRUE)
  )

# Print summaries
print(T_summary)
print(FCIb_summary)
print(IS_summary)
```




#Statistical comparison of years
```{r}

library(car)

GenIndices_all$T.. = as.numeric(GenIndices_all$T..)

# 1. Shapiro-Wilk test for normality in each year
shapiro_results <- GenIndices_all %>%
  group_by(Network) %>%
  summarise(
    W = shapiro.test(T..)$statistic,
    p_value = shapiro.test(T..)$p.value
  )

print("Shapiro-Wilk normality test per group:")
print(shapiro_results)

# 2. Levene's test for equal variances
print("Levene’s test for homogeneity of variances:")
levene_result <- leveneTest(T.. ~ Network, data = GenIndices_all)
print(levene_result)

# 3. Diagnostic plot (Q-Q)
ggplot(GenIndices_all, aes(sample = T..)) +
  stat_qq() + 
  stat_qq_line() + 
  facet_wrap(~ Network) +
  theme_minimal() +
  labs(title = "Q-Q plots for normality check")


# Kruskal–Wallis test
kruskal_test <- kruskal.test(T.. ~ Network, data = GenIndices_all)
print(kruskal_test)

# Pairwise Wilcoxon test with Holm correction
pairwise_wilcox <- pairwise.wilcox.test(GenIndices_all$`T..`, GenIndices_all$Network, 
                                        p.adjust.method = "holm")

print(pairwise_wilcox)

PathIndices_all$FCIb = as.numeric(PathIndices_all$FCIb)

# Kruskal–Wallis test
kruskal_test <- kruskal.test(FCIb ~ Network, data = PathIndices_all)
print(kruskal_test)

# Pairwise Wilcoxon test with Holm correction
pairwise_wilcox <- pairwise.wilcox.test(PathIndices_all$FCIb, PathIndices_all$Network, 
                                        p.adjust.method = "holm")

print(pairwise_wilcox)

link_weights_all$Variance_Link_Weight = as.numeric(link_weights_all$Variance_Link_Weight)

# Kruskal–Wallis test
kruskal_test <- kruskal.test(Variance_Link_Weight ~ Network, data = link_weights_all)
print(kruskal_test)

# Pairwise Wilcoxon test with Holm correction
pairwise_wilcox <- pairwise.wilcox.test(link_weights_all$Variance_Link_Weight, link_weights_all$Network, 
                                        p.adjust.method = "holm")

print(pairwise_wilcox)

```


#Manuscript plotting
```{r}
GenPlot_with_CI <- GenPlot_with_CI + 
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),  # Added this line
        plot.title = element_text(face = "plain", hjust = 0.5, size = 15),
        legend.position = "none",
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        panel.background = element_blank(),  # Corrected typo
        plot.background = element_blank()) +  # Corrected typo
  labs(y = expression("T.. (mmol C / m"^2*"/day)")) +
  annotate("text", x = -Inf, y = Inf, label = "A", hjust = -0.5, vjust = 1.5, size = 6, fontface = "bold")

variance_IS <- variance_IS + 
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),  # Added this line
        plot.title = element_text(face = "plain", hjust = 0.5, size = 15),
        legend.position = "none",
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        panel.background = element_blank(),  # Corrected typo
        plot.background = element_blank()) +  # Corrected typo
  labs(y = expression("IS (mmol C / m"^2*"/day)")) +
  annotate("text", x = -Inf, y = Inf, label = "C", hjust = -0.5, vjust = 1.5, size = 6, fontface = "bold")

PathPlot_with_CI <- PathPlot_with_CI + 
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),  # Added this line
        plot.title = element_text(face = "plain", hjust = 0.5, size = 15),
        legend.position = "none",
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        panel.background = element_blank(),  # Corrected typo
        plot.background = element_blank()) +  # Corrected typo
  labs(y = expression("FCIb (mmol C / m"^2*"/day)")) +
  annotate("text", x = -Inf, y = Inf, label = "B", hjust = -0.5, vjust = 1.5, size = 6, fontface = "bold")

production_plot <- production_plot +
  annotate("text", x = -Inf, y = Inf, label = "D", hjust = -0.5, vjust = 1.5, size = 6, fontface = "bold")

turbine_variables_plot <- turbine_variables_plot +
  annotate("text", x = -Inf, y = Inf, label = "E", hjust = -0.5, vjust = 1.5, size = 6, fontface = "bold")

# Arrange the plots
first_plot <- (GenPlot_with_CI | PathPlot_with_CI | variance_IS) + 
  plot_layout(ncol = 3, heights = c(1))

second_plot <- (production_plot + turbine_variables_plot) + 
  plot_layout(ncol = 2, heights = c(1))

final_plot <- first_plot / second_plot + 
  plot_layout(ncol = 1, heights = c(1, 1))

# Save the final plot
ggsave("~/phD/WP1_TemporalFW/manuscript/Figures/ENA_indices.jpg", plot = final_plot, dpi = 300, width = 15, height = 10)
```



#Carbon stocks

```{r, echo = F, fig.width=12, fig.height=5, echo = F, include = F, warning = F}
# Assume LIM.abril09 is your only LIM object
CstocksTot_09 <- round(LIM.abril09$Components$val, digits = 2)

# Convert to a data frame
CstocksTot_09 <- as.data.frame(t(CstocksTot_09 ))

# Assign row names (single row name for single data set)
rownames(CstocksTot_09) <- "Abril09"

# Assign column names
colnames(CstocksTot_09) <- LIM.abril09$Components$name

Cstocks_09 <- CstocksTot_09 %>%
  mutate(
    Detritus = rowSums(dplyr::select(., all_of(c("SOM", "SPOM", "SEDBAC", "WATBAC"))), na.rm = TRUE),
    Sediment = rowSums(dplyr::select(., all_of(c("DETAMPS", "BIVALVS", "FILTFEDSHRS", "CARPOLS", "THISCUS", "ECHCORS", "DETCARSHRS", "PAGURIS", "CEPHALS", "OPHIURS", "DETPOLRS", "CARCRAS", "ANTHOZOS"))), na.rm = TRUE),
    Ubiquous = rowSums(dplyr::select(., all_of(c("ASTRUBU", "PSAMMU", "DETCRARU", "CARPOLPU", "NEPHTYU", "NEMERTU"))), na.rm = TRUE),
    Plankton = rowSums(dplyr::select(., all_of(c("PHY", "ZOO"))), na.rm = TRUE),
    Fish = rowSums(dplyr::select(., all_of(c("PLEURO", "ECHVIP", "CALLSP", "POMSP", "AMMOD", "GADID", "MULSUR"))), na.rm = TRUE),
    Turbine = rowSums(dplyr::select(., all_of(c("METRIDTR", "CARCRATR", "SUSGASTR", "CARPOLTR", "SUDECRATR", "MYTILUTR", "NUDIBRTR", "BALANOTR", "JASSATR", "DETPOLTR", "BIVALVTR", "OPHIURTR", "LEPTRETR", "SDAMPTR"))), na.rm = TRUE)
  )


Cstocks_09  <- Cstocks_09  %>%
  dplyr::select(
    Detritus, 
    Turbine, Sediment, Ubiquous, Plankton, Fish)

CstockTot_09_long <- pivot_longer(Cstocks_09 , names_to = "Variable", values_to = "value", cols = everything())

# Define colors for the variables
Colors <- colors()[c(201, 496, 12, 142, 153, 157)]


# Assume LIM.abril12 is your only LIM object
CstocksTot_12 <- round(LIM.abril12$Components$val, digits = 2)

# Convert to a data frame
CstocksTot_12 <- as.data.frame(t(CstocksTot_12 ))

# Assign row names (single row name for single data set)
rownames(CstocksTot_12) <- "Abril12"

# Assign column names
colnames(CstocksTot_12) <- LIM.abril12$Components$name

Cstocks_12 <- CstocksTot_12 %>%
  mutate(
    Detritus = rowSums(dplyr::select(., "SOM", "SPOM", "SEDBAC", "WATBAC"), na.rm = TRUE),
    Turbine = rowSums(dplyr::select(., "LEPTRETR", "BALANOTR", "MYTILUTR", "CARPOLTR", "NUDIBRTR", "OPHIURTR", "DETPOLTR", "JASSATR", "DETCRATR", "METRIDTR", "DETAMPTR"), na.rm = TRUE),
    Sediment = rowSums(dplyr::select(., "CARPOLS", "CARCRAS", "HERBCRABS", "CEPHALS", "BIVALVS", "CUMACERS", "PAGURIS", "DETCARSHRS", "DETAMPS", "DETPOLRS", "OPHIURS", "ECHCORS", "ANTHOZOA"), na.rm = TRUE),
    Ubiquous = rowSums(dplyr::select(., "CARPOLPU", "NEMERTU", "HOMGAMU", "PSAMMU", "ASTRUBU", "NEPHTYU"), na.rm = TRUE),
    Plankton = rowSums(dplyr::select(., "PHY", "ZOO"), na.rm = TRUE),
    Fish = rowSums(dplyr::select(., "MULSUR", "AGONCAT", "AMMOD", "CALLSP", "GADID", "ECHVIP", "PLEURO"), na.rm = TRUE)
  ) 

Cstocks_12  <- Cstocks_12  %>%
  dplyr::select(
    Detritus, 
    Turbine, Sediment, Ubiquous, Plankton, Fish)

CstockTot_12_long <- pivot_longer(Cstocks_12 , names_to = "Variable", values_to = "value", cols = everything())

# Define colors for the variables
Colors <- colors()[c(201, 496, 12, 142, 153, 157)]

# Assume LIM.abril16 is your only LIM object
CstocksTot_16 <- round(LIM.abril16$Components$val, digits = 2)

# Convert to a data frame
CstocksTot_16 <- as.data.frame(t(CstocksTot_16 ))

# Assign row names (single row name for single data set)
rownames(CstocksTot_16) <- "Abril16"

# Assign column names
colnames(CstocksTot_16) <- LIM.abril16$Components$name

Cstocks_16 <- CstocksTot_16 %>%
  mutate(
    Detritus = rowSums(dplyr::select(., "SOM", "SPOM", "SEDBAC", "WATBAC"), na.rm = TRUE),
        Sediment = rowSums(dplyr::select(., "CARPOLS", "CARCRAS", "CUMACERS", "CEPHALS", "BIVALVS", "PAGURIS", "DETCARSHRS", "DETAMPS", "DETPOLRS", "OPHIURS", "ECHCORS", "THISCUS"), na.rm = TRUE),
    Turbine = rowSums(dplyr::select(.,"DETAMPTR", "OPHFRAT", "ANTHOZTR", "LEPTRETR", "BALANOTR", "CARPOLTR", "BIVALVTR", "CARCRATR", "JASSATR", "MYTILUTR", "METRIDTR", "SUDECRATR"), na.rm = TRUE),
    Ubiquous = rowSums(dplyr::select(., "GASTRU", "ASTRUBU", "PSAMMU", "NEMERTU", "NEPHTYU"), na.rm = TRUE),
    Fish = rowSums(dplyr::select(., "COTTIDAE", "TRIGLI", "POMSP", "AMMOD", "MULSUR", "CALLSP", "GADID", "ECHVIP", "PLEURO"), na.rm = TRUE),
    Plankton = rowSums(dplyr::select(., "PHY", "ZOO"), na.rm = TRUE)
  ) 

Cstocks_16  <- Cstocks_16  %>%
  dplyr::select(
   Detritus, 
    Turbine, Sediment, Ubiquous, Plankton, Fish)

CstockTot_16_long <- pivot_longer(Cstocks_16 , names_to = "Variable", values_to = "value", cols = everything())

#######

# Define colors for the variables
Colors <- colors()[c(201, 496, 12, 142, 153, 157)]

# Assume LIM.abril19 is your only LIM object
CstocksTot_19 <- round(LIM.abril19$Components$val, digits = 2)

# Convert to a data frame
CstocksTot_19 <- as.data.frame(t(CstocksTot_19 ))

# Assign row names (single row name for single data set)
rownames(CstocksTot_19) <- "Abril19"

# Assign column names
colnames(CstocksTot_19) <- LIM.abril19$Components$name

Cstocks_19 <- CstocksTot_19 %>%
  mutate(
    Detritus = rowSums(dplyr::select(., "SOM", "SPOM", "SEDBAC", "WATBAC"), na.rm = TRUE),
    
    Sediment = rowSums(dplyr::select(., "OPHIURS", "ANTHOZS", "ECHCORS", "DETCARSHRS", "DPAMPS", "PAGURIS", 
                              "CEPHALS", "CARCRAS", "CUMACERS", "THISCUS", "BIVALVS", "CARPOLS", 
                              "DETAMPS", "DETPOLRS"), na.rm = TRUE),
    
    Turbine = rowSums(dplyr::select(., "BIVALVTR", "SDAMPTR", "LEPTRETR", "DETPOLTR", "OPHIURTR", "BALANOTR", 
                             "MYTILUTR", "JASSATR", "CARCRATR", "SUSGASTR", "SUDECRATR", "CARPOLTR", 
                             "METRIDTR", "DETAMPTR"), na.rm = TRUE),
    
    Ubiquous = rowSums(dplyr::select(., "PSAMMU", "ASTRUBU", "NEPHTYU", "NEMERTU", "DETCRARU"), na.rm = TRUE),
    
    Fish = rowSums(dplyr::select(., "ZEUFA", "MULSUR", "POMSP", "COTTIDAE", "AMMOD", "TRIGLI", 
                          "CALLSP", "ECHVIP", "PLEURO"), na.rm = TRUE),
    Plankton = rowSums(dplyr::select(., "PHY", "ZOO"), na.rm = TRUE)
  ) 

Cstocks_19  <- Cstocks_19  %>%
  dplyr::select(
   Detritus, 
    Turbine, Sediment, Ubiquous, Plankton, Fish)

CstockTot_19_long <- pivot_longer(Cstocks_19 , names_to = "Variable", values_to = "value", cols = everything())

#######

# Assume LIM.abril22 is your only LIM object for 2022
CstocksTot_22 <- round(LIM.abril22$Components$val, digits = 2)

# Convert to a data frame
CstocksTot_22 <- as.data.frame(t(CstocksTot_22))

# Assign row names (single row name for single data set)
rownames(CstocksTot_22) <- "Abril22"

# Assign column names
colnames(CstocksTot_22) <- LIM.abril22$Components$name

# Calculate the categories with updated compartments
Cstocks_22 <- CstocksTot_22 %>%
  mutate(
    Detritus = rowSums(dplyr::select(., all_of(c("SOM", "SPOM", "SEDBAC", "WATBAC"))), na.rm = TRUE),
    
    # Sediment (updated with new compartments)
    Sediment = rowSums(dplyr::select(., all_of(c("DETAMPS", "ECHCORS", "CARCRAS", "OPHIURS", "DETPOLRS", "DETCARSHRS", 
                                                "CARPOLS", "THISCUS", "BIVALVS", "CUMACERS", "CEPHALS", 
                                                "ANTHOZOS"))), na.rm = TRUE),

    # Ubiquous (updated with new compartments)
    Ubiquous = rowSums(dplyr::select(., all_of(c("ASTRUBU", "PSAMMU", "NEMERTU", "GASTRU", "DETCRARU", "NEPHTYU"))), na.rm = TRUE),

    # Plankton category remains the same as before
    Plankton = rowSums(dplyr::select(., all_of(c("PHY", "ZOO"))), na.rm = TRUE),

    # Fish (updated with new compartments)
    Fish = rowSums(dplyr::select(., all_of(c("ECHVIP", "PLEURO", "MULSUR", "GADID", "POMSP", "CALLSP", "AMMOD"))), na.rm = TRUE),
    
    # Turbine (updated with new compartments)
    Turbine = rowSums(dplyr::select(., all_of(c("METRIDTR", "SUSGASTR", "MYTILUTR", "SDAMPTR", "CARPOLTR", "SUDECRATR", "BIVALVTR", 
                                                "DETPOLTR", "BALANOTR", "LEPTRETR", "JASSATR", "OPHIURTR", "CARCRATR", "DETAMPTR"))), na.rm = TRUE)
  )

# Select relevant columns (Detritus, Turbine, Sediment, Ubiquous, Plankton, Fish)
Cstocks_22  <- Cstocks_22  %>%
  dplyr::select(
    Detritus, 
    Turbine, Sediment, Ubiquous, Plankton, Fish)

# Reshape to long format
CstockTot_22_long <- pivot_longer(Cstocks_22 , names_to = "Variable", values_to = "value", cols = everything())

max_value <- 400

Colors <- c("Turbine" = "#0072B2",    # Blue
            "Ubiquous" = "#E69F00",   # Orange
            "Sediment" = "#009E73",   # Green
            "Fish" = "#D55E00",       # Red-Orange
            "Plankton" = "#CC79A7") 
            
Cstocks09_plot2 <- ggplot(CstockTot_09_long, aes(fill = Variable, y = value, x = "")) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = Colors) +
  ylab(expression(paste("C stocks 2009 [mmol C m "^-2, "]"))) +
  xlab("") +
  theme_minimal(base_size = 10) +
  theme(text = element_text(size = 10)) +
  scale_color_viridis_d() +
  theme(axis.text = element_text(size = 10), axis.title.x = element_blank()) +
  theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size = 10)) +
  ylim(0, max_value)

# Plot for 2012
Cstocks12_plot2 <- ggplot(CstockTot_12_long, aes(fill = Variable, y = value, x = "")) + 
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_manual(values = Colors) +
  ylab(expression(paste("C stocks 2012 [mmol C m "^-2, "]"))) +
  xlab("") +
  theme_minimal(base_size = 10) +
  theme(text = element_text(size = 10)) +
  scale_color_viridis_d() +
  theme(axis.text = element_text(size = 10), axis.title.x = element_blank()) +
  theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size = 10)) +
  ylim(0, max_value)

# Plot for 2016
Cstocks16_plot2 <- ggplot(CstockTot_16_long, aes(fill = Variable, y = value, x = "")) +
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_manual(values = Colors) +
  ylab(expression(paste("C stocks 2016 [mmol C m "^-2, "]"))) +
  xlab("") +
  theme_minimal(base_size = 10) +
  theme(text = element_text(size = 10)) +
  scale_color_viridis_d() +
  theme(axis.text = element_text(size = 10), axis.title.x = element_blank()) +
  theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size = 10)) +  
  ylim(0, max_value)

Cstocks19_plot2 <- ggplot(CstockTot_19_long, aes(fill = Variable, y = value, x = "")) +
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_manual(values = Colors) +
  ylab(expression(paste("C stocks 2019 [mmol C m "^-2, "]"))) +
  xlab("") +
  theme_minimal(base_size = 10) +
  theme(text = element_text(size = 10)) +
  scale_color_viridis_d() +
  theme(axis.text = element_text(size = 10), axis.title.x = element_blank()) +
  theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size = 10)) +  
  ylim(0, max_value)

Cstocks22_plot2 <- ggplot(CstockTot_22_long, aes(fill = Variable, y = value, x = "")) +
  geom_bar(position = "stack", stat = "identity") +
  scale_fill_manual(values = Colors) +
  ylab(expression(paste("C stocks 2022 [mmol C m "^-2, "]"))) +
  xlab("") +
  theme_minimal(base_size = 10) +
  theme(text = element_text(size = 10)) +
  scale_color_viridis_d() +
  theme(axis.text = element_text(size = 10), axis.title.x = element_blank()) +
  theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size = 10)) +  
  ylim(0, max_value)


# Add a "Year" column to each dataset
CstockTot_09_long$Year <- "2009"
CstockTot_12_long$Year <- "2012"
CstockTot_16_long$Year <- "2016"
CstockTot_19_long$Year <- "2019"
CstockTot_22_long$Year <- "2022"

# Combine all datasets into one
CstockTot_all <- rbind(CstockTot_09_long, CstockTot_12_long, CstockTot_16_long, CstockTot_19_long, CstockTot_22_long)


Total_carbon2 <- ggplot(CstockTot_all, aes(fill = Variable, y = value, x = Year)) + 
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = Colors) +
  ylab(expression(paste("C stocks [mmol C m "^-2, "]"))) +
  xlab("Year") +
  theme_minimal(base_size = 10) +
  theme(text = element_text(size = 10),
        axis.text = element_text(size = 10),
        axis.title.x = element_text(size = 10)) +
  theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size = 10)) +
  ylim(0, max_value)


print(Total_carbon2)


```

### Sample diagnostics

There are two types of diagnostics:
- Plots: you visualize how good the sampling space is sampled
- Diagnostic: are used to asses statistical convergence. 

A lot of those plots and diagnostics are done at the level of flows, therefore, we have around 500 plots to visually check, therefore, sometimes diagnostics are more easy.

1. Check sample coverage and whether jumpsize is ok
```{r}
##################
samplerange <- data.frame(Rangesabril22)
samplerange$samplemin <- apply(results_2022, 2, min)
samplerange$samplemax <- apply(results_2022, 2, max)
samplerange$percCover <- ((samplerange$samplemax - samplerange$samplemin) / (samplerange$max - samplerange$min) * 100)
#print(samplerange, digits = 2)
 
# Mean percentage covered range
mean(samplerange$percCover, na.rm = T)

##################
samplerange <- data.frame(Rangesabril19)
samplerange$samplemin <- apply(results_2019, 2, min)
samplerange$samplemax <- apply(results_2019, 2, max)
samplerange$percCover <- ((samplerange$samplemax - samplerange$samplemin) / (samplerange$max - samplerange$min) * 100)
#print(samplerange, digits = 2)
 
# Mean percentage covered range
mean(samplerange$percCover, na.rm = T)

##################
samplerange <- data.frame(Rangesabril16)
samplerange$samplemin <- apply(results_2016, 2, min)
samplerange$samplemax <- apply(results_2016, 2, max)
samplerange$percCover <- ((samplerange$samplemax - samplerange$samplemin) / (samplerange$max - samplerange$min) * 100)
#print(samplerange, digits = 2)
 
# Mean percentage covered range
mean(samplerange$percCover, na.rm = T)

##################
samplerange <- data.frame(Rangesabril12)
samplerange$samplemin <- apply(results_2012, 2, min)
samplerange$samplemax <- apply(results_2012, 2, max)
samplerange$percCover <- ((samplerange$samplemax - samplerange$samplemin) / (samplerange$max - samplerange$min) * 100)
#print(samplerange, digits = 2)
 
# Mean percentage covered range
mean(samplerange$percCover, na.rm = T)

##################
samplerange <- data.frame(Rangesabril09)
samplerange$samplemin <- apply(results_2009, 2, min)
samplerange$samplemax <- apply(results_2009, 2, max)
samplerange$percCover <- ((samplerange$samplemax - samplerange$samplemin) / (samplerange$max - samplerange$min) * 100)
#print(samplerange, digits = 2)
 
# Mean percentage covered range
mean(samplerange$percCover, na.rm = T)

```


**The Raftery and Lewis diagnostic**

The main principle behind the Raftery and Lewis diagnostic is that a correct sample of the objective distribution, here the uniform distribution, should give precise estimates of its quantiles. Usually the 0.025 quantile is used.

This diagnostic provides multiple pieces of information, such as the burning value (M), an estimate of the sample size to ensure precise estimation of a prescribed quantile (N), a lower bound (Nmin), and a dependence factor (I).

The dependance factor assesses the extent to which auto-correlation inflates the required sample size; values larger than 5 indicate a strong auto-correlation.

```{r}
q <- 0.025
RL <- coda::raftery.diag(data = results_2012, q=q)
RL
```

**The Geweke diagnostic**

The Geweke diagnostic is a classical statistical test of comparison of means applied to prescribed proportions of the first and last points generated by an MCMC algorithm. For each variable, a value $Z$ is computed, the hypothesis of convergence of the algorithm is rejected if $\left| Z \right|$ exceeds a prescribed quantile of the normal distribution. With $p_1 = 0.1$ and $p_2 = 0.5$, convergence is rejected when $\left| Z \right| \geq 1.28$.  f the flow has reached stationarity, the means of the two parts
will be equal (Plummer et al., 2020), reflected by a Geweke Z-score
between −1.96 and 1.96 (corresponding to p = 0.05).

Evalautes stationarity, values should be between -1.96 and 1.96

```{r}
frac1 <- 0.1
frac2 <- 0.5
G <- coda::geweke.diag(results_2009, frac1 = frac1, frac2 = frac2)
G

# Subset flows where Z < -1.96 or Z > 1.96
flows_outside_1.96 <- G$z[G$z < -1.28 | G$z > 1.28]

# Visualize the subset
print(flows_outside_1.96)
```

**Heidelberger and Welch's convergence diagnostic**
Determines the stationary of the variables in the MCMC chain and burn-in periods.
It first tests the stationary of the sample chain and he second (halfwidth test) tests if there are enough samples to estimate the mean of the flow values with an acceptable degree of precision.

```{r}
coda::heidel.diag(results_2009)
```

**Effective Sample Size**

The Effective Sample Size (ESS) reflects the amount of autocorrelation in the MCMC draws. The closer ESS is to N (the sample size), the better, since it means that the draws are lowly auto-correlated.
ESS > 10% of total iterations

```{r}

#Get total number of iterations
total_iters <- nrow(results_2009[[1]])

#Get effective sample sizes
ess <- coda::effectiveSize(results_2009)

#Identify flows with ESS < 10% of total iterations
low_ess_flows <- ess[ess < 0.1 * total_iters]

print(low_ess_flows)

```

**Kernel density plots**
Shows the sample PDF p(x) where stationarity can be iferrred if P(x) approaches the underlying soluton space of PDF q(x). You expect a gaussian disttribution if the flow is properly sampled.

**Trace plot and autocorrelation plots**
Shows the mixing and autocorelation plots. You expect a catepillat for a well sampled flow.  Trace plots show the
sampled value of a flow at each iteration of the MCMC chain. A well-
sampled flow looks like a ’hairy caterpillar’ (Roy, 2020) i.e., a visually
random pattern that indicates good mixing (van den Meersche et al.,
2009) (Fig. 4 H).

Autocorrelation plots indicate correlation between successive solutions and, therefore, the proportion of samples that can
be considered ‘independent’ (Hogg and Foreman-Mackey, 2018). Specifically, the plots show the lag-k (sample) autocorrelation between k
steps apart (Roy, 2020). For fast mixing MCMC chains, lag-k autocorrelation values drop to zero almost as quickly as k increases (Roy, 2020) (Fig. 4 I).

*Run mean plots* 
Test the sample efficiency. If it does not stabilize at a fixed value, then more iterations are needed.

```{r}
results = as.data.frame(results_2009)
mcmc_plots(results, flow = "JASSATR->SPOM")
```

#Check the convergence of the results
```{r}
## Convergence
## convergence function

 convergence <- function(Bay  = NULL,
                         stp  = NULL,
                         flow = flow)
  {                       
  sdevs <- vector("numeric",stp)
  means <- vector("numeric",stp)
  n     <- nrow(Bay)
  for (i in 1:stp){
    random   <-sort(runif(n),index.return=TRUE) 
    sdevs[i] <-   sd(Bay[random$ix[1:(i*(n/stp))],flow])
    means[i] <- mean(Bay[random$ix[1:(i*(n/stp))],flow])
    }
  plot(seq(from=n/stp,n,by=n/stp),means,xlab="No of solutions",ylab="flow value",main=colnames(Bay)[flow],sub="mean")
  plot(seq(from=n/stp,n,by=n/stp),sdevs,xlab="No of solutions",ylab="flow value",main=colnames(Bay)[flow],sub="st. devs")
  
  return(cbind(means, sdevs))
  
 }

 par(mfrow=c(2,2))
 stp   <- 1000  #step with increase of solutions
 flow <- which(colnames(results_2009)==names(sort(colMaxs(results_2009),decreasing = TRUE)[1]))
 result_maxflow <- convergence(Bay=results_2009, stp= 1000 ,flow=flow)
 flow  <- which(colnames(results_2009)==names(sort(colMins(results_2009)[which(colMins(results_2009)>0)],decreasing = FALSE)[1]))
 result_minflow <- convergence(Bay=results_2009, stp= 1000 ,flow=flow)
 var(result_maxflow[2:50,"sdevs"])
var(result_maxflow[2:1000,"sdevs"])
 var(result_maxflow[2:1000,"sdevs"])/var(result_maxflow[2:50,"sdevs"])*100
var(result_minflow[2:50,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])/var(result_minflow[2:50,"sdevs"])*100
 
  par(mfrow=c(2,2))
 stp   <- 1000  #step with increase of solutions
 flow <- which(colnames(results_2012)==names(sort(colMaxs(results_2012),decreasing = TRUE)[1]))
 result_maxflow <- convergence(Bay=results_2012, stp= 1000 ,flow=flow)
 flow  <- which(colnames(results_2012)==names(sort(colMins(results_2012)[which(colMins(results_2012)>0)],decreasing = FALSE)[1]))
 result_minflow <- convergence(Bay=results_2012, stp= 1000 ,flow=flow)
 var(result_maxflow[2:50,"sdevs"])
 var(result_maxflow[2:1000,"sdevs"])
var(result_maxflow[2:1000,"sdevs"])/var(result_maxflow[2:50,"sdevs"])*100
 var(result_minflow[2:50,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])/var(result_minflow[2:50,"sdevs"])*100
 
   par(mfrow=c(2,2))
 stp   <- 1000  #step with increase of solutions
 flow <- which(colnames(results_2016)==names(sort(colMaxs(results_2016),decreasing = TRUE)[1]))
 result_maxflow <- convergence(Bay=results_2016, stp= 1000 ,flow=flow)
 flow  <- which(colnames(results_2016)==names(sort(colMins(results_2016)[which(colMins(results_2016)>0)],decreasing = FALSE)[1]))
 result_minflow <- convergence(Bay=results_2016, stp= 1000 ,flow=flow)
var(result_maxflow[2:50,"sdevs"])
 var(result_maxflow[2:1000,"sdevs"])
 var(result_maxflow[2:1000,"sdevs"])/var(result_maxflow[2:50,"sdevs"])*100
 var(result_minflow[2:50,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])/var(result_minflow[2:50,"sdevs"])*100
 
    par(mfrow=c(2,2))
 stp   <- 1000  #step with increase of solutions
 flow <- which(colnames(results_2019)==names(sort(colMaxs(results_2019),decreasing = TRUE)[1]))
 result_maxflow <- convergence(Bay=results_2019, stp= 1000 ,flow=flow)
 flow  <- which(colnames(results_2019)==names(sort(colMins(results_2019)[which(colMins(results_2019)>0)],decreasing = FALSE)[1]))
 result_minflow <- convergence(Bay=results_2019, stp= 1000 ,flow=flow)
var(result_maxflow[2:50,"sdevs"])
 var(result_maxflow[2:1000,"sdevs"])
 var(result_maxflow[2:1000,"sdevs"])/var(result_maxflow[2:50,"sdevs"])*100
 var(result_minflow[2:50,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])/var(result_minflow[2:50,"sdevs"])*100
 
    par(mfrow=c(2,2))
 stp   <- 1000  #step with increase of solutions
 flow <- which(colnames(results_2022)==names(sort(colMaxs(results_2022),decreasing = TRUE)[1]))
 result_maxflow <- convergence(Bay=results_2022, stp= 1000 ,flow=flow)
 flow  <- which(colnames(results_2022)==names(sort(colMins(results_2022)[which(colMins(results_2022)>0)],decreasing = FALSE)[1]))
 result_minflow <- convergence(Bay=results_2022, stp= 1000 ,flow=flow)
var(result_maxflow[2:50,"sdevs"])
 var(result_maxflow[2:1000,"sdevs"])
 var(result_maxflow[2:1000,"sdevs"])/var(result_maxflow[2:50,"sdevs"])*100
 var(result_minflow[2:50,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])
 var(result_minflow[2:1000,"sdevs"])/var(result_minflow[2:50,"sdevs"])*100
 
 

```



